A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-10 src/paper.tex
WIP:Web environment

The front controller architectural design pattern~\cite{Buschmann2007} is employed to centralize requests processing in a single component. Each second screen client sends requests to and receives responses from a single URL, what simplifies application development.

>>>>

\subsection{Web Environment}
\label{ssub_web_environment}

Request handling is carried out by using the front controller architectural design pattern~\cite{Buschmann2007}. It is employed to centralize requests processing in a single component. Each second screen client sends requests to and receives responses from a single URL, what simplifies application development.
